\thesistitle

### 2019-08-16 icse/paper.tex
Added some results
Should also remove some though

\subsection{Clone context}
% How many clones are there in certain contexts? Experiments for relation, location, and context.
To determine the refactoring method(s) that can be used to refactor most clones, we perform statistical analysis on the clone context (see Sec.~\ref{sec:context}).

>>>>

\subsection{Clone context}
% How many clones are there in certain contexts? Experiments for relation, location, and context.
To determine the refactoring method(s) that can be used to refactor most clones, we perform statistical analysis on the context of clones (see Sec.~\ref{sec:context}).

### 2019-08-16 sections/experimentalsetup.tex
This part keeps boggling my mind
Added some results
Should also remove some though

\subsection{Calculating a maintainability score}\label{sec:metricformula}
In this study, we use four metrics to determine maintainability (see Section~\ref{sec:metrics}). For our experiments, we aggregate the scores obtained by these metrics to draw a conclusion about the maintainability increase or decrease after applying a refactoring. We base our aggregation on the following assumptions:
\begin{itemize}
  \item All metrics are equal in terms of weight towards system maintenance effort.
  \item Higher values for the metrics imply lower maintainability.
  \item The obtained increase of the metric divided by the average distance from zero over our corpus weights the metric equally against the other metrics.
\end{itemize}
We derived these assumptions partly from Heitlager et al~\cite{heitlager2007practical} and our own expert intuition. The validity of these metrics influences the validity of the conclusions we can draw from our data. Because of that, in our experiments we focus mainly on significant differences in maintainability to draw a conclusion.

By dividing the obtained metric scores by the average distance from zero of all obtained values for a specific metric, we ensure that each metric is weighted equally towards the final maintainability score. We calculate the average distance from zero for all obtained values over our corpus as follows:
\begin{equation}\label{eq:scoredev}
A = \frac{\sum_{x \in M} abs(x)}{|M|}
\end{equation}
Where \textit{M} is the multiset of all metric increase/decrease values for all refactorings applied to a certain metric over our corpus. \textit{|M|} is the cardinality of this multiset. We then calculate the maintainability for a specific refactoring as follows:
\begin{equation}\label{eq:scoreref}
A_M = \frac{dup}{A_{dup}} + \frac{com}{A_{com}} + \frac{par}{A_{par}} + \frac{vol}{A_{vol}}
\end{equation}
Where \textit{dup} is the decrease in duplication, \textit{com} is the decrease in complexity, \textit{par} is the decrease is method parameters and \textit{vol} is the decrease in system volume after the refactoring is applied. When comparing the maintainability of a set of refactorings we divide the sum of the maintainability score by the amount of clone instances of all refactored clones in the set.

>>>>

\section{Calculating a maintainability score}\label{sec:metricformula}
In this study, we use four metrics to determine maintainability (see Section~\ref{sec:metrics}). For our experiments, we aggregate the scores obtained by these metrics to draw a conclusion about the maintainability increase or decrease after applying a refactoring. We base our aggregation on the following assumptions:
\begin{itemize}
  \item All metrics are equal in terms of weight towards system maintenance effort.
  \item Higher values for the metrics imply lower maintainability.
  \item The obtained increase of the metric divided by the average distance from zero over our corpus weights the metric equally against the other metrics.
\end{itemize}
We derived these assumptions partly from Heitlager et al~\cite{heitlager2007practical} and our own expert intuition. The validity of these metrics influences the validity of the conclusions we can draw from our data. Because of that, in our experiments we focus mainly on significant differences in maintainability to draw a conclusion.

By dividing the obtained metric scores by the average distance from zero of all obtained values for a specific metric, we ensure that each metric is weighted equally towards the final maintainability score. We calculate this average distance as follows:
\begin{equation}\label{eq:scoredev}
A = \frac{\sum_{x \in M} abs(x)}{|M|}
\end{equation}
Where \textit{M} is the multiset of all metric increase/decrease values for all refactorings applied to a certain metric over our corpus. \textit{|M|} is the cardinality of this multiset. We then calculate the maintainability for a specific refactoring as follows:
\begin{equation}\label{eq:scoreref}
A_M = \frac{dup}{A_{dup}} + \frac{com}{A_{com}} + \frac{par}{A_{par}} + \frac{vol}{A_{vol}}
\end{equation}
Where \textit{dup} is the decrease in duplication, \textit{com} is the decrease in complexity, \textit{par} is the decrease is method parameters and \textit{vol} is the decrease in system volume after the refactoring is applied. When comparing the maintainability of a set of refactorings we divide the sum of the maintainability score by the amount of clone instances of all refactored clones in the set.

### 2019-08-16 sections/results.tex
working on various things
Added some results
Should also remove some though

\chapter{Results}\label{ch:results}
In this chapter, we present the results of our experiments.

@@

\section{Thresholds} \label{sec:thresholds}
\todo{todo}

\section{Context Analysis of Clones}\label{chap:clonecontextexpl}
We analyzed the context of clones in a large corpus of open source projects. For these experiments, we used our CloneRefactor tool. These experiments follow the structure of the context: The relation between clone instances is explained, measured and discussed in chapter \ref{chap:relationsinstances}; the location of clone instances is explained, measured and discussed in chapter \ref{chap:clonelocation};  he content of clone instances are explained, measured and discussed in chapter \ref{chap:clonecontents}.

@@

\section{Clone instance contents}\label{chap:clonecontents}
\todo{update these results}
Measuring the clone contents categories defined in Section~\ref{sec:setupcontents} yields the results displayed in Table \ref{table:contents}.

>>>>

\chapter{Results}\label{ch:results}
In this chapter, we present the results of our experiments. All these results were obtained using CloneRefactor.

@@

\subsection{Clone context}
% How many clones are there in certain contexts? Experiments for relation, location, and context.
To determine the refactoring method(s) that can be used to refactor most clones, we perform statistical analysis on the context of clones (see Sec.~\ref{sec:context}).

\subsubsection{Relation}
Table~\ref{tab:relation} displays the number of clone classes found for the entire corpus for different relations (see Sec.~\ref{sec:relation}).

\begin{table}[H]
\centering
\begin{tabular}{@{}llll@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{Relation}} & \textit{\textbf{Clone Classes}} & \textit{\textbf{Total}} \\ \midrule
\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Class\end{tabular}} & Same Class & 22,893 & \multirow{2}{*}{31,848} \\ \cmidrule(lr){2-3}
 & Same Method & 8,955 &  \\ \midrule
\multirow{5}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Hierarchy\end{tabular}} & Sibling & 15,588 & \multirow{5}{*}{20,342} \\ \cmidrule(lr){2-3}
 & Superclass & 2,616 &  \\ \cmidrule(lr){2-3}
 & First Cousin & 1,219 &  \\ \cmidrule(lr){2-3}
 & Common Hierarchy & 720 &  \\ \cmidrule(lr){2-3}
 & Ancestor & 199 &  \\ \midrule
\multirow{4}{*}{Unrelated} & No Direct Superclass & 10,677 & \multirow{4}{*}{20,314} \\ \cmidrule(lr){2-3}
 & External Superclass & 4,525 &  \\ \cmidrule(lr){2-3}
 & External Ancestor & 3,347 &  \\ \cmidrule(lr){2-3}
 & No Indirect Superclass & 1,765 &  \\ \midrule
\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Interface\end{tabular}} & Same Direct Interface & 7,522 & \multirow{2}{*}{13,074} \\ \cmidrule(lr){2-3}
 & Same Indirect Interface & 5,552 &  \\ \bottomrule
\end{tabular}
\caption{Number of clone classes per clone relation}
\label{tab:relation}
\end{table}

\subsubsection{Contents}
Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different contents (see Sec.~\ref{sec:contents}).

\begin{table}[H]
\centering
\begin{tabular}{@{}llll@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{Contents}} & \textit{\textbf{Clone instances}} & \textit{\textbf{Total}} \\ \midrule
\multirow{2}{*}{Partial} & Partial Method & 219,540 & \multirow{2}{*}{229,521} \\ \cmidrule(lr){2-3}
 & Partial Constructor & 9,981 &  \\ \midrule
\multirow{5}{*}{Full} & Full Method & 12,990 & \multirow{5}{*}{13,173} \\ \cmidrule(lr){2-3}
 & Full Interface & 64 &  \\ \cmidrule(lr){2-3}
 & Full Constructor & 58 &  \\ \cmidrule(lr){2-3}
 & Full Class & 37 &  \\ \cmidrule(lr){2-3}
 & Full Enum & 24 &  \\ \midrule
\multirow{3}{*}{Other} & Several Methods & 22,749 & \multirow{3}{*}{53,773} \\ \cmidrule(lr){2-3}
 & Only Fields & 17,700 &  \\ \cmidrule(lr){2-3}
 & Other & 13,324 &  \\ \bottomrule
\end{tabular}
\caption{Number of clone instances for clone contents categories}
\label{tab:contents}
\end{table}

\subsection{Extract Method}
%To what extent can found clones be refactored through method extraction, without requiring additional transformations.
Table~\ref{tab:refactorability} shows to what extent clone classes can be refactored by using the ``Extract Method'' refactoring technique. The second column shows our measurements for the complete systems (just like the former experiments). The third column shows our measurements when restricting our search to method bodies. The amount that can be extracted increases because, when restricting our search to method bodies, we do not exclude declarations that can obstruct the possibility of method extraction (for instance a cloned method signature).

\begin{table}[H]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{All}} & \textit{\textbf{Method Body}} \\ \midrule
Can Be Extracted & 24,157 & 26,109 \\
Is Not A Partial Method & 21,625 & 0 \\
Top-level AST-Node is not a Statement & 19,887 & 4,607 \\
Spans Part of a Block & 12,964 & 13,460 \\
Multiple Return Values & 5,622 & 6,131 \\
Complex Control Flow & 1,106 & 1,216 \\ \bottomrule
\end{tabular}
\caption{Number of clones that can be extracted using the ``Extract Method'' refactoring technique}
\label{tab:refactorability}
\end{table}

\subsection{Refactoring}
%I think the ultimate goal with this thesis is to do experiments with different clone thresholds. Which thresholds give clones that we should refactor? For this, we will measure the maintainability of the refactored source code over different thresholds. These thresholds range from minimum clone size, variability, and gap size.
In our corpus, CloneRefactor has refactored 12.710 clone classes and measured the change in indicated metrics (see Sec.~\ref{sec:metrics}). Using the presented formulas (see Sec.~\ref{sec:metricformula}) we determine how the characteristics of the extracted method (see Sec.~\ref{sec:characteristics}) influence the maintainability of the resulting codebase after refactoring. In this section, we explore the data received by comparing the before- and after snapshots of the system for each separate refactoring.

\subsubsection{Clone Token Volume}
Figure \ref{fig:duplication} shows the obtained results when plotting the clone size (in tokens) vs the maintainability increase/decrease. On the secondary axis the amount of refactorings that have refactored a clone with the specified amount of tokens is displayed (e.g. the amount of data points the data is based on). As the amount of data points decreases, the datapoints gain less statistical significance.

\begin{figure*}
  \includegraphics[width=1\textwidth]{img/duplication}
  \caption{A graph that shows how the size in tokens of the refactored clone affects maintainability. Maintainability on the primary axis and amount of refactorings on the secondary axis.}
  \label{fig:duplication}
\end{figure*}

The volume of the clone is the dominating factor regarding the maintainability increase/decrease of cloned code. Because of that, for our further experiments, we filter out all refactorings with a token size smaller than 18 because otherwise the small clones dominate the results and turn all results towards unmaintainable.

\subsubsection{Relation}
Table~\ref{tab:relation_refactor} shows our data regarding how different relations influence maintainability. We have marked rows based on less than 100 refactorings red, as their result does not have statistical significance.

\begin{table}[]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
\textit{\textbf{Relation}} & \textit{\textbf{\begin{tabular}[c]{@{}l@{}}Maintainability\\ Score\end{tabular}}} & \textit{\textbf{\begin{tabular}[c]{@{}l@{}}Number of\\ Refactorings\end{tabular}}} \\ \midrule
\textbf{Common Hierarchy} & \textbf{0.51} & \textbf{792} \\ \midrule
\hspace{10pt} Sibling & 0.57 & 637 \\
\rowcolor[HTML]{FFCCC9}
\hspace{10pt} Same Hierarchy & 0.55 & 22 \\
\rowcolor[HTML]{FFCCC9}
\hspace{10pt} Superclass & 0.20 & 74 \\
\rowcolor[HTML]{FFCCC9}
\hspace{10pt} First Cousin & -0.02 & 53 \\
\rowcolor[HTML]{FFCCC9}
\hspace{10pt} Ancestor & -0.65 & 6 \\ \midrule
\textbf{Common Class} & \textbf{0.01} & \textbf{2,025}\\ \midrule
\hspace{10pt} Same Method & 0.01 & 762  \\
\hspace{10pt} Same Class & 0.01 & 1,263 \\ \midrule
\textbf{Unrelated} & \textbf{-0.02} & \textbf{688}\\ \midrule
\hspace{10pt} No Direct Superclass & 0.08 & 289 \\
\hspace{10pt} External Superclass & -0.02 & 225  \\
\rowcolor[HTML]{FFCCC9}
\hspace{10pt} No Indirect Superclass & -0.04 & 30  \\
\hspace{10pt} External Ancestor & -0.26 & 144  \\ \midrule
\textbf{Common Interface} & \textbf{-0.11} & \textbf{283} \\ \midrule
\hspace{10pt} Same Direct Interface & 0.02 & 160 \\
\hspace{10pt} Same Indirect Interface & -0.31 & 123
\end{tabular}
\caption{Influence on maintainability of refactoring clones by certain relations.}
\label{tab:relation_refactor}
\end{table}

\subsubsection{Return Value}
Table~\ref{tab:return} shows how the return value of the extracted method influences the maintainability of the resulting system.

\begin{table}[H]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
\textit{\textbf{Return Value}} & \begin{tabular}[c]{@{}l@{}}\textit{\textbf{Maintainability}}\\\textit{\textbf{Score}}\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textit{\textbf{Number of}}\\\textit{\textbf{Refactorings}}\end{tabular} \\ \midrule
Return & 0.20 & 421 \\
Void & 0.19 & 2052 \\
Declare & 0.03 & 1318 \\
\rowcolor[HTML]{FFCCC9}
Assign & -1.29 & 3 \\ \bottomrule
\end{tabular}
\caption{Maintainability scores for different return values}
\label{tab:return}
\end{table}

\subsubsection{Parameters}
Fig.~\ref{fig:arguments} shows how an increase in parameters lowers the maintainability of the refactored code. On the primary x-axis, the maintainability is displayed. The secondary x-axis shows the number of refactorings. The y-axis shows the number of parameters.

\begin{figure}[H]
  \includegraphics[width=1\columnwidth]{img/arguments}
  \caption{Influence of number of method parameters on system maintainability.}
  \label{fig:arguments}
\end{figure}

\section{Context Analysis of Clones}\label{chap:clonecontextexpl}
We analyzed the context of clones in a large corpus of open source projects. These experiments follow the structure of the context: The relation between clone instances is explained, measured and discussed in chapter \ref{chap:relationsinstances}; the location of clone instances is explained, measured and discussed in chapter \ref{chap:clonelocation};  he content of clone instances are explained, measured and discussed in chapter \ref{chap:clonecontents}.

@@

\subsection{Clone instance contents}\label{chap:clonecontents}
\todo{update these results}
Measuring the clone contents categories defined in Section~\ref{sec:setupcontents} yields the results displayed in Table \ref{table:contents}.
